MinCall --- MinION od raw signala do genoma

### 2017-05-05 paper/main.tex
Whatever

\voditelj{Mile Sikić}
\title{MinCall --- MinION  basecaller pogonjen dubokim ucenjem}
\engtitle{MinCall --- MinION deep learning powered basecaller}
\author{Neven Miculinić}

@@

\begin{sazetak}
TODO

\kljucnerijeci{TODO}
\end{sazetak}

@@

    Whole process is trainned end-to-end from raw signal on R9 sequecing pore and once trainned it's independent from Metrichor.
\keywords{}
\end{abstract}

>>>>

\voditelj{Mile Sikić}
\title{MinCall --- MinION od raw signala do genoma}
\engtitle{MinCall --- MinION end2end deep learning basecaller}
\author{Neven Miculinić}

@@

\begin{sazetak}

\kljucnerijeci{Basecaller, MinION, sekvenciniranje sljedece generacije}
\end{sazetak}

@@

    Whole process is trainned end-to-end from raw signal on R9 sequecing pore and once trainned it's independent from Metrichor.
\keywords{Basecaller, MinION, R9, CNN, CTC, Next generation sequecing}
\end{abstract}
